A parallelised and distributed approach to implementing Conway's Game of Life

### 2022-12-05 report/article_2.tex
added single worker v single thread report

As an initial attempt, we began by implementing a 
single-threaded Game of Life (GoL) Engine, expanding upon this work 
with parallelisation by virtue of concurrent go-routine workers. 
Recognising that there exists various methods to calculating the perimeter
for \texttt{getNeighbourCount}, we tried various counting methods - taking into 
account the wrap-around feature of Game of Life.

@@

\section{Distributed Implementation}

>>>>

As an initial attempt, we began by implementing a 
single-threaded Game of Life (GoL) Engine, expanding upon this work 
with parallelisation by virtue of concurrent go-routine workers. 
Recognising that there exists various methods to calculating the perimeter
for \texttt{getNeighbourCount}, we tried various counting methods - taking into 
account the modularity of Game of Life - as well as finding channel alternatives.

@@

\section{Distributed Implementation}
Similar to how we did the parallel side, we started the distributed section by using a single worker, this time
with the worker being a separate process and communicated to via Remote Procedure Calls (RPC henceforth). This expanded to
doing using multiple workers, implementing fault tolerance and finally halo exchange.

%------------------------------------------------
\section{A lonesome worker}
\subsection{Logic}
Our single-worker distributed implementation moved much of the processing to said worker. From the distributor, we sent a 
single RPC call to the worker, processed GoL turns on the worker, then sent the final state back. Results are shown in Fig. 5.
\begin{figure}
  \includegraphics[width=\linewidth]{para-v-dist.png}
  \caption{1 worker vs. 1 thread}
  \label{fig:chart5}
\end{figure}
\subsection{On the topic of Analysis 4}
The differences between the benchmark times is not significant when compared to multi-threaded work. We 
identified an average of 4.54\% time decrease, which is most likely attributed to how the single-threaded workload had 
go-routines for Alive Cells and Key presses, whereas the single worker was Step 1 of Distributed, being "barebones".
